Synthesizing Quotient Lenses

### 2017-10-17 papers/QuotientLensSynth/main.tex
More comments

\section{Introduction}
{\em Bidirectional programming languages} such as
Boomerang~\cite{boomerang}, Augeas~\cite{augeas}, XSugar~\cite{xsugar},
biXid~\cite{bixid} and X/Inv~\cite{xinv}enable a programmer to express a
transformation that maps some input data to some output data, as well as a
transformation that maps the output data back into the input data in a single
expression. An example of a {\em bidirectional transformation} which we shall
revisit severally in this paper is a program which converts citation records
such as
\begin{verbatim}
@Book {conway,
  Author = "J. H. Conway",
  Title = {Regular Algebra and Finite Machines}
}
\end{verbatim}

>>>>

\section{Introduction}
\bcp{Not sure there is time to fix this, but the intro seems very long and
  technical---it takes a long time to get to saying what our actual
  contributions are!  Wonder if we should move most of it to a second
  ``Example'' section.} 
{\em Bidirectional programming languages} such as
Boomerang~\cite{boomerang}, Augeas~\cite{augeas}, XSugar~\cite{xsugar},
biXid~\cite{bixid} and X/Inv~\cite{xinv}enable a programmer to express a
transformation that maps some input data to some output data, as well as a
transformation that maps the output data back into the input data in a single
expression. An example of a {\em bidirectional transformation} which we shall
revisit severally in this paper is a program which converts citation records
such as
\begin{verbatim}
@Book {conway,
  Author = "J. H. Conway",
  Title = {Regular Algebra and Finite Machines}
}
\end{verbatim}
